Water discharge has a variable impact on sediment transport capacity in subglacial systems

### 2023-08-17 Delaneyetal2023b.tex
Updates from Overleaf

In natural systems, variable mobilization and deposition of sediment occur as water and sediment discharge accumulate as they move through the two-dimensional channel network will compound the already substantial variability in sediment mobilization parameters accounted for here in the lumped parameterization.
Such variability could be especially strong in the subglacial system where melt water pathways change in response to the evolving hydraulic gradient \citep{delaney2023}.

>>>>

In natural systems, variable mobilization and deposition of sediment occur as water and sediment discharge accumulate as they move through the two-dimensional channel network will compound the already substantial variability in sediment mobilization parameters accounted for here in the lumped parameterization.
Such variability could be especially strong in the subglacial system where meltwater pathways change in response to the evolving hydraulic gradient \citep{delaney2023}.
